---
title: "Experiment 2: Perspective perception experiment"
author: "Bodo Winter, Julius Hassemer"
date: "9/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preprocessing

This is the analysis for Experiment 2. We begin by loading the necessary libraries.

```{r libraries, message = FALSE}
library(tidyverse)
library(stringr)
library(MuMIn)
```

Next, load in the data.

```{r E2_data_entry}
E2 <- read.csv('../data/E2.csv',
               fileEncoding = 'latin1')
```

Let's rename the really ugly column names (thanks Qualtrics!).

```{r E2_renaming}
E2 <- rename(E2,
             Response = The.gesture.you.just.saw.characterized.an.object..Ê.What.do.you.think.the.gesture.was.about.,
             ObjectCondition = Display.Order..Block.Randomizer.FL_3,
             Control = What.is.4...17..Please.type.in.your.answer.,
             Age = What.is.your.age.,
             Gender = What.is.your.gender.,
             Handedness = Are.you.left.or.right.handed.,
             Language = What.is.your.native.language...your.native.languages..Your.native.language.s..is.what.you.spoke.a...)
```

Let's get only those columns that we need:

```{r subset_cols}
E2 <- select(E2,
             Response,
             ObjectCondition,
             Control,
             Age,
             Gender,
             Handedness,
             Language)
```

Since we used read.csv, let's make things into characters:

```{r char_convert}
E2 <- mutate(E2,
             Response = as.character(Response),
             ObjectCondition = as.character(ObjectCondition),
             Control = as.character(Control),
             Age = as.character(Age),
             Gender = as.character(Gender),
             Handedness = as.character(Handedness),
             Language = as.character(Language))
```

Check the number of data points:

```{r check_N}
nrow(E2)
```

Get rid of Ju's test response and those that got the math question (sanity check) wrong:

```{r clean}
E2 <- filter(E2,
             Control != 'JuTest',
             Control == '21')
nrow(E2)
```

Take only those that are native speakers (actually, this step doesn't matter as much as this is essentially a nonlinguistic task — but we want to make sure that people understood the questions right and that the sample corresponds to a well-defined population of interest). Bilinguals are included, so long as they list English first.

```{r native_speakers}
these_langs <- c('Italian', 'Japanese, English', 'Russian',
	'Serbian', 'Spanish and English', 'tamil, english', 'German', 'none',
	'Serbian ')
E2 <- filter(E2, !(Language %in% these_langs))
nrow(E2)
```

How many men/women?

```{r gender_check}
table(E2$Gender)
```

Create a response column, as well as a numerical version of it, with shape as reference level ("towards height").

```{r create_response}
E2 <- mutate(E2,
             Response = str_extract(Response, 'shape|height'),
             Resp01 = ifelse(Response == 'height', 1, 0))
```

Separate the condition column so that we have the information for the separate conditions in separate columns.

```{r sep_conds}
E2 <- separate(E2, col = ObjectCondition,
	into = c('Perspective', 'Tilt', 'PinkieCurl'),
	remove = FALSE)
```

Explanation: "Tilt" is discussed as "Viewing Angle" in the paper, "Perspective" is discussed as "Viewing Direction".

Create a numerical pinkie curl variable and center this variable:

```{r pinkie_num}
E2 <- mutate(E2,
             PinkieCurl = as.numeric(as.factor(PinkieCurl)),
             PinkieCurl_c = PinkieCurl - mean(PinkieCurl))
```

Check randomization:

```{r randomization_check}
table(E2$Perspective)
table(E2$Tilt)
table(E2$PinkieCurl)
table(E2$Perspective, E2$PinkieCurl)
table(E2$Perspective, E2$Tilt)
table(E2$PinkieCurl, E2$Tilt)
```

Looks all nice and balanced.

This is how the PinkieCurl is coded:

- small values = high curl
- large values = big extension

1 is maximally curled in and 9 is maximally extended. So in effect, this is an extension variable.

## Descriptive values

Let's look at the data descriptively:

```{r descriptive_summaries}
# Perspective:

E2 %>% group_by(Perspective) %>%
  summarize(Height = mean(Resp01))

# Tilt:

E2 %>% group_by(Tilt) %>%
  summarize(Height = mean(Resp01))

# Pinkie curl:

E2 %>% group_by(PinkieCurl) %>%
  summarize(Height = mean(Resp01)) %>% 
  mutate(Shape = 1 - Height)
```

Descriptive values by tilt and perspective (for plot).

```{r tilt_and_persp_means}
E2 %>% group_by(Perspective, Tilt) %>%
  summarize(Height = round(mean(Resp01), 2))
```

## Setting up predictors

We should sum-code perspective, since it's going to feature in interactions. We'll also make Tilt into a numeric variable since the steps are equal-sized.

```{r code_predictors}
E2 <- mutate(E2,
             Perspective_c = as.numeric(as.factor(Perspective)) - 2,
             Tilt_c = as.numeric(as.factor(Tilt)) - 2)
```

In Hassemer and Winter (2016), we found a quadratic pattern for pinkie curl. So we'll create a quadratic predictors:

```{r pinkie_quadr}
E2 <- mutate(E2,
             PinkieCurl_c2 = PinkieCurl_c ^ 2)
```

## Analysis

The main model that is reported is the following:

```{r main_model}
xmdl <- glm(Resp01 ~ PinkieCurl_c + PinkieCurl_c2 +
              Perspective_c + Tilt_c,
            E2, family = 'binomial')
summary(xmdl)
```

Check the coefficients for reporting:

```{r main_model_coefs}
# Estimates:

summary(xmdl)$coefficients[, 1]

# Standard errors:

summary(xmdl)$coefficients[, 2]

# Reverse for reporting (more intuitive this way) and compute odds:

exp(summary(xmdl)$coefficients[, 1] * -1)
```

In addition, let's assess whether there are any interactions:

```{r interact_model}
xmdl.interact <- glm(Resp01 ~
                       (PinkieCurl_c + PinkieCurl_c2) *
                       (Perspective_c + Tilt_c) +
                       PinkieCurl_c:Perspective_c:Tilt_c +
                       PinkieCurl_c2:Perspective_c:Tilt_c,
                     E2, family = 'binomial')
summary(xmdl.interact)

# Test all of them in one likelihood ratio test:

anova(xmdl, xmdl.interact, test = 'Chisq')
```

Let's create the null models for likelihood ratio tests.

```{r null_models}
xmdl.nopinkie <- glm(Resp01 ~
                       Perspective_c + Tilt_c,
                     E2, family = 'binomial')
xmdl.nopinkie.noquadr <- glm(Resp01 ~
                               Perspective_c + Tilt_c + PinkieCurl_c,
                             E2, family = 'binomial')
xmdl.nopersp <- glm(Resp01 ~
                      PinkieCurl_c + PinkieCurl_c2 + Tilt_c,
                    E2, family = 'binomial')
xmdl.notilt <- glm(Resp01 ~
                     Perspective_c + PinkieCurl_c + PinkieCurl_c2,
                   E2, family = 'binomial')
```

Let's perform likelihood ratio tests:

```{r likelihood_ratio_tests}
# Test pinkie curl, quadratic and linear together:

anova(xmdl.nopinkie, xmdl, test = 'Chisq')

# Only quadratic pinkie curl effect:

anova(xmdl.nopinkie.noquadr, xmdl, test = 'Chisq')

# Only linear pinkie curl effect:

anova(xmdl.nopinkie, xmdl.nopinkie.noquadr, test = 'Chisq')

# Perspective effect:

anova(xmdl.nopersp, xmdl, test = 'Chisq')

# Tilt effect:

anova(xmdl.notilt, xmdl, test = 'Chisq')
```

# Assess R-squared

```{r}
# Full model:

r.squaredGLMM(xmdl)

# Pinkie curl effect:

r.squaredGLMM(xmdl)[1] - r.squaredGLMM(xmdl.nopinkie)[1]

# Perspective effect:

r.squaredGLMM(xmdl)[1] - r.squaredGLMM(xmdl.nopersp)[1]

# Tilt effect:

r.squaredGLMM(xmdl)[1] - r.squaredGLMM(xmdl.notilt)[1]
```

# Derive model predictions

Let's get the model predictions for the significant Perspective effect. First, we define the new data frame with values to derive predictions for. Then we use predict()

```{r persp_preds}
newdata_persp <- data.frame(PinkieCurl_c = 0,
                      PinkieCurl_c2 = 0,
                      Tilt_c = 0,
                      Perspective_c = c(-1, 1))

## Check predictions:

plogis(predict(xmdl, newdata_persp))
```

Next, we check the predictions for the significant Pinkie Curl effect:

```{r pinkie_preds}
uniques <- sort(unique(E2$PinkieCurl_c))
newdata_pinkie <- data.frame(PinkieCurl_c = uniques,
                      Tilt_c = 0,
                      Perspective_c = 0) %>%
  mutate(PinkieCurl_c2 = PinkieCurl_c ^ 2)
newdata_pinkie$Height <- plogis(predict(xmdl, newdata_pinkie))
newdata_pinkie$Height

```

Let's get the upper and lower confidence bands for this (for plot):

```{r pinke_preds_CI}
# Standard errors:

SEs <- predict(xmdl, newdata_pinkie, se.fit = TRUE)$se.fit

# 2 times standard errors:

SE2 <- predict(xmdl, newdata_pinkie, se.fit = TRUE)$se.fit * 2

# Log odds:

logits <- predict(xmdl, newdata_pinkie, se.fit = TRUE)$fit

# Upper and lower bounds:

newdata_pinkie$UB <- logits + SE2
newdata_pinkie$LB <- logits - SE2

# Check:

select(newdata_pinkie, -Tilt_c, -Perspective_c)
```


